\newcommand{\qone}{
Develop a Python program that reads marks from three different subjects and calculates their average.
}

\newcommand{\qtwo}{
Create a Python script to convert weight from kilograms to pounds.
}

\newcommand{\qthree}{
Write a program that takes the lengths of the three sides of a prism as input (integers) and computes its surface area using the formula: 2ab + 2bc + 2ca.
}

\newcommand{\qfour}{
Design a Python program to calculate the speed of a plane, given a distance of 395,000 meters and a travel time of 9,000 seconds.
}

\newcommand{\qfive}{
Build a program that determines how long it will take to empty a swimming pool of dimensions $12m × 7m × 2m$ using a pump with a flow rate of 17 cubic meters per hour.
}

\newcommand{\qsix}{
Write a Python script to convert temperature from Celsius to Fahrenheit (input as a float).
}

\newcommand{\qseven}{
Create a program to compute the total number of seconds in one full day.
}

\newcommand{\qeight}{
 Develop a Python program to calculate the acceleration of a car that starts from rest and reaches a velocity of 10 m/s in 20 seconds, using the formula: (vfinal - vinitial)/time.
}

\newcommand{\qnine}{
Write a program to display Pascal’s triangle.
}

\newcommand{\qten}{
Write a program to display the following pattern using nested loops.\\
1 1\\
22 21\\
333 321\\
4444 4321\\
55555 54321
}

\newcommand{\qeleven}{
Write a program that uses a while loop to add up all the even numbers between 100 and 200.
}

\newcommand{\qtwelve}{
Write a program to print the sum of the following series

a. $1 + \frac{1}{2} + \frac{1}{3} +. …. + \frac{1}{n}$

b. $\frac{1}{1} + \frac{2^2}{2} + \frac{3^3}{3} +. …. + \frac{n^n}{n}$
}

\newcommand{\qthirteen}{
Write a program to find the depreciation value of an asset (property) by reading the purchase value of the asset (amt), year of the service (year) and the value of depreciation.
}

\newcommand{\qfourteen}{
Write a program that accepts a string from the user and display the same string after removing vowels from it.
}

\newcommand{\qfifteen}{
Write a function to insert a string in the middle of the string.
}

\newcommand{\qsixteen}{
Write a program to sort a string lexicographically.
}

\newcommand{\qseventeen}{
Write a program to replace a string with another string without using built-in methods.
}

\newcommand{\qeighteen}{
 Write a program to concatenate two strings into another string without using the + operator.
}

\newcommand{\qnineteen}{
 Write a program to strip a set of characters from a string.
}

\newcommand{\qtwenty}{
 Write a program to extract the first n characters of a string.
}

\newcommand{\qtwentyone}{
Write a program that creates a list of 10 random integers. Then create two lists by name odd list and even list that have all odd and even values of the list respectively.
}

\newcommand{\qtwentytwo}{
Write a program to sort the elements in ascending order using insertion sort.
}

\newcommand{\qtwentythree}{
 Write a Python program to use binary search to find the key element in the list.
}

\newcommand{\qtwentyfour}{
Make a list of the first eight letters of the alphabet, then using the slice operation do the following operations:\\
a. Print the first three letters of the alphabet.
b. Print any three letters from the middle.\\
c. Print the letters from any particular index to the end of the list.
}

\newcommand{\qtwentyfive}{
Write a program to sort the elements in ascending order using selection sort.
}

\newcommand{\qtwentysix}{
 Write a program that prints the maximum value of the second half of the list.
}

\newcommand{\qtwentyseven}{
Write a program that creates a list of numbers 1–100 that are either divisible by 5 or 6.
}

\newcommand{\qtwentyeight}{
Write a function that prompts the user to enter five numbers, then invoke a function to find the GCD of these numbers.
}

\newcommand{\qtwentynine}{
 Write a function named addfruit, which is passed with a set of fruit names and their prices and returns a dictionary containing the entered information and raises a ValueError exception if the fruit is already present.
}

\newcommand{\qthirty}{
 Write a function to add the air quality index as the value and the date as the key; create the dictionary for the entered information.
}

\newcommand{\qthirtyone}{
Create a dictionary that contains usernames as the key and passwords as the associated values. Make up the data for five dictionary entries and demonstrate the use of clear and fromkeys() methods.
}

\newcommand{\qthirtytwo}{
Write Pythonic code to create a dictionary that accepts a country name as a key and its capital city as the value. Display the details in sorted order.
}

\newcommand{\qthirtythree}{
Write a program that has the dictionary of your friends’ names as keys and phone numbers as its values. Print the dictionary in a sorted order. Prompt the user to enter the name and check if it is present in the dictionary. If the name is not present, then enter the details in the dictionary.
}

\newcommand{\qthirtyfour}{
Write a program to create a dictionary containing the author name as the keys and ISBN number as the value. Make up the data for five dictionary entries and demonstrate the use of clear() and fromkeys() methods.
}

\newcommand{\qthirtyfive}{
Create a list containing three elements, and then create a tuple from that list.
}

\newcommand{\qthirtysix}{
Write a program to unpack a tuple to several variables.
}

\newcommand{\qthirtyseven}{
Write a program to check whether an item exists within a tuple.
}

\newcommand{\qthirtyeight}{
Write a program to unzip a list of tuples into individual lists.
}

\newcommand{\qthirtynine}{
Write a program to create an intersection, union, set difference, and symmetric difference of sets.
}

\newcommand{\qforty}{
Write a program to demonstrate the use of issubset() and issuperset() methods.
}

\newcommand{\qfortyone}{
Write a program that takes a range and creates a list of tuples within that range with the first 
element as the number and the second element as the square of the number.
}

\newcommand{\qfortytwo}{
Write a program to clear a set.
}

\newcommand{\qfortythree}{
 Write a program to find the length of the set.
}

\newcommand{\qfortyfour}{
Write a program to store the latitude and longitude of your house as a tuple and display it.
}

\newcommand{\qfortyfive}{
Write a program that prompts the user to enter a text file, reads words from the file, and displays all the non-duplicate words in ascending order.
}

\newcommand{\qfortysix}{
Write a program to get the file size of a plain text file.
}

\newcommand{\qfortyseven}{
Write a program that prompts the user to enter a text filename and displays the number of vowels and consonants in the file.
}

\newcommand{\qfortyeight}{
Write a program to read the first n lines of a file. Prompt the user to enter the value for n.
}

\newcommand{\qfortynine}{
Write a program that reads the contents of the file and counts the occurrences of each letter. Prompt the user to enter the filename.
}

\newcommand{\qfifty}{
Write a program to read the last n lines of a file. Prompt the user to enter the value for n.
}

\newcommand{\qfiftyone}{
Write a program to combine each line from the first file with the corresponding line in the second file.
}

\newcommand{\qfiftytwo}{
Write a program to remove newline characters from a file.
}

\newcommand{\qfiftythree}{
Write a program to read the random line from a file.
}

\newcommand{\qfiftyfour}{
Write a program to read and write the contents from one csv file to another.
}

\newcommand{\qfiftyfive}{
Write a Python program that matches a word containing 'z'.
}

\newcommand{\qfiftysix}{
Write a Python program to remove all leading zeros' from an IP address
}

\newcommand{\qfiftyseven}{
Write a Python program to search the numbers (0–9) of length between 1 to 3 in a given string.
}

\newcommand{\qfiftyeight}{
Write a Python program to find the substrings within a string
}

\newcommand{\qfiftynine}{
Write a Python program to extract year, month and date from an url.
}

\newcommand{\qsixty}{
Write a Python program to read a file and to convert a date of yyyy-mm-dd format to dd-mm-yyyy format.
}

\newcommand{\qsixtyone}{
Write a Python program to abbreviate 'Street' as 'St.' in a given string.
}

\newcommand{\qsixtytwo}{
Write a Python program to find all five characters long word in a string.
}

\newcommand{\qsixtythree}{
Create a class named quadratic, where a, b, c are data attributes and the methods are

a. \_\_init()\_\_ to initialize the data attributes\\
b. roots() to compute the quadratic equation
}

\newcommand{\qsixtyfour}{
Define a class called student. Display the marks details of top five students using inheritance.
}

\newcommand{\qsixtyfive}{
Create a class called library with data attributes like acc\_number, publisher, title and author. The methods of the class should include

a. read() – acc\_number, title, author.

b. compute() - to accept the number of days late, calculate and display the fine charged at the rate of \$1.50 per day.
}

\newcommand{\qsixtysix}{
Create two base classes named clock and calendar. Based on these two classes define a class calendarclock, which inherits from both the classes which displays month details, date and time.
}

\newcommand{\qsixtyseven}{
Write a program to add two polynomials using classes.
}

\newcommand{\qsixtyeight}{
Define JSON. Construct a simple JSON document and write Pythonic code to parse JSON document.
}

\newcommand{\qsixtynine}{
Elaborate on the differences between XML and JSON.
}

\newcommand{\qseventy}{
Define XML. Construct a simple XML document and write Python code to loop through XML nodes in the document.
}

\newcommand{\qseventyone}{
Explain NumPy array creation functions with examples.
}

\newcommand{\qseventytwo}{
Explain NumPy integer indexing, array indexing, Boolean array indexing and slicing with examples.
}

\newcommand{\qseventythree}{
 Write Python program to create and display a one-dimensional array-like object containing an array of data using pandas library.
}

\newcommand{\qseventyfour}{
Write Python program to add, subtract, multiply and divide two Pandas Series.
}

\newcommand{\qseventyfive}{
Write Python program to create and display a Data Frame from a dictionary data which has the index labels.
}

\newcommand{\qseventysix}{
Find the eigenvalues of a $3\times3$ matrix.
}

\newcommand{\qseventyseven}{
Write a NumPy program to compute the dot product of two vectors.
}

\newcommand{\qseventyeight}{
Given a Pandas DataFrame, remove duplicate rows based on a specific column.
}

\newcommand{\qseventynine}{
Create a checkerboard matrix of size $10\times10$$ using NumPy.
}

\newcommand{\qeighty}{
Plot a scatter plot with regression line using Altair.
}

\newcommand{\qeightyone}{
Compute the covariance matrix of a dataset using NumPy.
}

\newcommand{\qeightytwo}{
Group a DataFrame by two columns and compute aggregate statistics.
}

\newcommand{\qeightythree}{
Create a cumulative sum column in a Pandas DataFrame.
}

\newcommand{\qeightyfour}{
Generate 1000 random numbers from a normal distribution and plot histogram using Altair.
}

\newcommand{\qeightyfive}{
Write a function to standardize a NumPy array (mean 0, variance 1).
}

\newcommand{\qeightysix}{
Reshape a 1D NumPy array into a 3D array of appropriate dimensions.
}

\newcommand{\qeightyseven}{
Merge three DataFrames on a common key.
}

\newcommand{\qeightyeight}{
Create an interactive Altair chart with dropdown selection filter.
}

\newcommand{\qeightynine}{
Detect and remove outliers using Z-score method in Pandas.
}

\newcommand{\qninety}{
Compute pairwise correlation matrix of a DataFrame.
}

\newcommand{\qninetyone}{
Create a heatmap visualization using Altair.
}

\newcommand{\qninetytwo}{
Apply a custom function to each element of a NumPy array using vectorization.
}

\newcommand{\qninetythree}{
Convert a categorical column into one-hot encoding using Pandas.
}

\newcommand{\qninetyfour}{
Perform left, right, inner, and outer joins between two DataFrames.
}

\newcommand{\qninetyfive}{
Create a rolling window standard deviation column in Pandas.
}

\newcommand{\qninetysix}{
Plot multiple layered charts in Altair with shared axes.
}

\newcommand{\qninetyseven}{
Calculate percentile values of a NumPy array.
}

\newcommand{\qninetyeight}{
Create a time-series line chart with tooltips in Altair.
}

\newcommand{\qninetynine}{
Split a DataFrame into training and testing sets using random sampling.
}

\newcommand{\qonehundred}{
Load a CSV file using Pandas, clean missing data, compute summary statistics with NumPy, and visualize results using Altair.
}